Challenges to transboundary fisheries management in North America under climate

### 2020-05-03 Ecol/Manuscript_Draft.Rmd
Changes for thesis chapter

---
title: Challenges to transboundary fisheries management in North America under climate
  change
author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
date: ^1^ Institute for the Oceans and Fisheries, University of British Columbia,
  Vancouver, Canada
output:
  bookdown::pdf_book:
    toc : false
  # pdf_document: default
  # word_document: default
editor_options:
  chunk_output_type: console
csl: ../References/E&S.csl
subtitle: '[Response to Reviewers]'
bibliography: ../References/Oceans_Canada_Biblio.bib
---

@@

```{r Figure1-map, eval = T, echo=FALSE, fig.pos= "H", fig.height = 4, fig.width = 6, fig.cap="Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement"}

@@

```{r Figure2-NA, eval = T, echo=FALSE, fig.pos= "H", fig.cap="Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario. Points represent areas where at least one model do not agree in the direction of change"}

@@

```{r Figure-4-iphc-prop, eval = T, echo = F, fig.pos= "H", fig.height = 6, fig.width = 4,  fig.cap = "Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014. Values represent the mean of 3 ESM; error bars represent +- sd."}

@@

```{r Figure5-goma, eval = T, echo = F, fig.pos = "H", fig.height = 4, fig.width = 6, fig.cap = "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014). Points represent regions where models do not agree in direction of change."}

@@

```{r Figure-6-goma-prop, eval = T, echo = F, fig.pos = "L", fig.cap = "Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present. Values represent the mean of 3 ESM; error bars represent +- sd. (2005-2014)."}

@@

```{r Figure-S1, eval = T, echo = F, fig.pos= "H", fig.cap = "Variation of climate change scenarios"}

@@

```{r Figure_S2, eval = T, echo = F, fig.pos= "H", fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}

@@

```{r Figure_S3, eval = T, echo = F, fig.pos= "H", fig.cap = "Outliers GoMA"}

>>>>

---
output:
  bookdown::pdf_book:
    toc : false
  # pdf_document: default
  # word_document: default
editor_options:
  chunk_output_type: console
csl: ../References/E&S.csl
bibliography: ../References/Oceans_Canada_Biblio.bib
header-includes: #allows you to add in your own Latex packages
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h
---

@@

```{r Figure1-map, eval = T, echo=FALSE, fig.height = 4, fig.width = 6, fig.cap="Map of North America with the regulatory areas of the International Paific Halibut Comission and the NAFO sub-region containing the Gulf of Maine arrangement"}

@@

```{r Figure2-NA, eval = T, echo=FALSE, fig.cap="Percentage change of MCP of transboundary stocks of North America for mid $21^{st}$ century (2041-2060) relative to present (2005-2014) under a A) high emission scenario and; B) low emission scenario. Points represent areas where at least one model do not agree in the direction of change"}

@@

```{r Figure-4-iphc-prop, eval = T, echo = F, fig.height = 6, fig.width = 4,  fig.cap = "Percentage change of stock-share ratio for IPHC under A) high emission scenario and B) low emission scenario for mid 21st century (2041-2060) relative to present 2005-2014. Values represent the mean of 3 ESM; error bars represent +- sd."}

@@

```{r Figure5-goma, eval = T, echo = F, fig.height = 4, fig.width = 6, fig.cap = "Percentage change of MCP in the Gulf of Maine under, A) high emission scenario; and B) low emission for mid-century (2041-2060) relative to present (2005-2014). Points represent regions where models do not agree in direction of change."}

@@

```{r Figure-6-goma-prop, eval = T, echo = F, fig.cap = "Changes in MCP stock-share ratio for Gulf of Maine under (A) high emission; and (B) low emission scenarios for mid 21st century (2041-2060) relative to present. Values represent the mean of 3 ESM; error bars represent +- sd. (2005-2014)."}

@@

```{r Figure-S1, eval = T, echo = F, fig.cap = "Variation of climate change scenarios"}

@@

```{r Figure_S2, eval = T, echo = F, fig.cap = "Variation of climate change scenarios in IPHC regions 4E and 4D"}

@@

```{r Figure_S3, eval = T, echo = F, fig.cap = "Outliers GoMA"}
